### 2022-03-11 paper/localpsf.tex
moded impulse response moments definition into its own section in the intro. Added normalized local mean displacement invariance discussion

In this paper we form hierarchical matrix approximations of operators $\Aop$ with locally supported, non-negative impulse responses that are accessible matrix-free.
\begin{description}
	\item[Locally supported impulse responses:] For all $x\in \Omega$, the support of $\impulseresponse_x$ is contained (or approximately contained) in a localized region.
	\item[Non-negative impulse responses:] We have
	\begin{equation*}
	\impulseresponse_x(y) \ge 0
	\end{equation*}
	for all (or approximately all) $(y,x) \in \Omega \times \Omega$.
	\item[Matrix-free:] One cannot easily evaluate kernel entries $\Aker(y,x)$. Instead, access to $\Aop$ is available through ``operator actions.'' That is, we have a black-box computational procedure (which is typically expensive) through which we may evaluate the maps
	\begin{equation*}
	u \mapsto\Aop u \quad \text{and} \quad v \mapsto \Aop^Tv
	\end{equation*} 
	for arbitrary functions $u$ and $v$. After discretization (see Appendix \ref{app:discretized_operations}), $\Aop$ becomes a dense matrix, $\bm{A}$, that is typically too large to be built and stored. This property is called ``matrix-free'' because at the discrete level it means that one can perform matrix-vector products of $\bm{A}$ and $\bm{A}^T$ with arbitrary vectors, but one cannot easily\footnote{One could compute $\bm{v} = \bm{A}\bm{e}_j$, where $\bm{e}_j=(0,\dots,0,1,0,\dots,0)$ is the unit vector which has $j^\text{th}$ component equal to one and all other components equal to zero, then extract $\bm{A}_{ij} = \bm{v}_i$. However, this process is wasteful because one computes the entire vector $\bm{v}$, then discards all but one component.} access matrix entries $\bm{A}_{ij}$. In applications, applying $\bm{A}$ to a vector may involve iteratively solving a large linear system, timestepping, or performing some other nontrivial computational procedure. 
	%For example, in reduced space approaches to PDE-constrained optimization and inverse problems, Hessian information is available only through the application of the Hessian to vectors, and one such Hessian application requires solving two PDEs \cite{HESSIANADJOINT}. 
\end{description}

@@

The impulse response $\impulseresponse_x$ may be interpreted as a scaled probability distribution because of the non-negative impulse response property. Let $\spatialvol:\Omega \rightarrow \mathbb{R}$,
\begin{equation*}
\spatialvol(x) := \int_\Omega \impulseresponse_x(y) dy
\end{equation*}
denote the spatially varying scaling factor (the ``volume'' of $\impulseresponse_x$), let 
\begin{equation}
\label{eq:scaled_impulse_response}
\widehat{\impulseresponse}_x := \impulseresponse_x / \spatialvol(x)
\end{equation}
denote the normalized version of $\impulseresponse_x$, and let $\mu:\Omega \rightarrow \mathbb{R}^d$, $\Sigma:\Omega \rightarrow \mathbb{R}^{d \times d},$
\begin{equation*}
\spatialmean(x) := \mathbb{E}(\widehat{\impulseresponse}_x), \qquad
\spatialcov(x) := \Var(\widehat{\impulseresponse}_x),
\end{equation*}
denote the spatially varying mean and covariance of $\widehat{\impulseresponse}_x$, respectively.

\subsection{Volume preconditioned local mean-displacement invariance}
\label{eq:local_mean_displacement_invariance}

Let $x$ and $x'$ be points in $\Omega$ that are ``close'' to each other, and consider the following four approximations, ordered by increasing level of sophistication:
\begin{align}
\phi_x(y) &\approx \phi_{x'}(y) \label{eq:translate1}\\
\phi_x(y) &\approx \phi_{x'}(y-x+x') \label{eq:translate2}\\
\phi_x(y) &\approx \phi_{x'}\left(y-\mu(x)+\mu(x')\right) \label{eq:translate3}\\
\frac{\phi_x(y)}{V(x)} &\approx \frac{\phi_{x'}\left(y-\mu(x)+\mu(x')\right)}{V(x')}. \label{eq:translate4}
\end{align}
Approximation \eqref{eq:translate1} says that $\phi_x$ can be approximated by $\phi_{x'}$ when $x$ and $x'$ are close. 
%This approximation follows from the assumption that $\Phi$ is smooth. 
Operators satisfying \eqref{eq:translate1} can be well-approximated via low-rank interpolative factorization/Nystrom approximation of $\Phi$ \cite{CUR,NYSTROM}.
% of the form
%\begin{equation}
%	\label{eq:low_rank_interpolation}
%	\Phi(y,x) \approx \sum_{i=1}^r w_i(x) \phi_{x_i}(y)
%\end{equation}
%where $\phi_{x_i}$ are known impulse responses at a collection of points $x_i$ scattered throughout $\Omega$, and $w_i$ are smooth weighting functions that interpolate the $\phi_{x_i}$. 
%In problems of practical interest, \eqref{eq:translate1} typically holds \emph{asymptotically} in the limit as $x'$ approaches $x$. 
However, 
%even if $\Phi$ is smooth (which is typically the case asymptotically),
%the relevant Lipschitz constant for continuity, and hence 
the required rank in the low rank approximation can be large, which makes algorithms based on assumption \eqref{eq:translate1} computationally expensive. This is the case for Hessians in PDE constrained inverse problems with highly informative data, as discussed in Section \ref{sec:PDE_hessian_motivation}. 
%As the data become more informative, typically the ``mass'' of $\Phi(y,x)$ concentrates nearer and nearer to the ``diagonal'' $y=x$, the Lipschitz constant increases, and the required rank in the approximation increases.
%Moreover, if $\Aop$ is numerically low rank, then one would typically use more accurate and robust matrix-free methods for forming low-rank approximations, such as randomized SVD or Lanczos.

@@

Our method is based on approximation \eqref{eq:translate3}, which is an improvement upon \eqref{eq:translate1} and \eqref{eq:translate2} that generalizes both. We call \eqref{eq:translate3} ``local mean-displacement invariance,'' and illustrate \eqref{eq:translate3} in Figure \ref{fig:mean_displacement_invariance}. On one hand, if \eqref{eq:translate1} holds, then $\mu(x) \approx \mu(x')$, and so \eqref{eq:translate3} holds. On the other hand, translating a distribution translates its mean, so if \eqref{eq:translate2} holds, then $\mu(x')-\mu(x) \approx x' - x$, so again \eqref{eq:translate3} holds. But approximation \eqref{eq:translate3} can hold in situations where neither \eqref{eq:translate1} nor \eqref{eq:translate2} holds. For example, because the expected value commutes with affine transformations, \eqref{eq:translate3} will hold when an $\Aop$ is locally translation-invariant with respect to a rotated frame of reference, while \eqref{eq:translate2} will not hold in this case. Additionally, \eqref{eq:translate3} generalizes to operators $\Aop:L^2(\Omega_1) \rightarrow L^2(\Omega_2)'$ that map between function spaces on different domains $\Omega_1$ and $\Omega_2$, and even operators that map between domains with different spatial dimensions. In contrast, \eqref{eq:translate2} does not naturally generalize to operators that map between function spaces on different domains, because the formula $y-x+x'$ requires vectors in $\Omega_2$ and $\Omega_1$ to be added together.

@@

Once the scattered impulse responses $\impulseresponse_{x_i}$ are computed, we approximate the integral kernel $\Phi(y,x)$ at arbitrary points $(y,x)$ by interpolation. The details of the interpolation will be described in Section \ref{sec:approximate_kernel_entries}, but the key principle behind the interpolation is the local mean displacement invariance assumption discussed in Section \ref{eq:local_mean_displacement_invariance}.
%Specifically, we make the assumption that
%\begin{equation}
%\Phi(y,x) = \phi_x(y) \approx \phi_{x_i}(y - \mu(x) + \mu(x_i))
%\end{equation}
%if $x_i$ is close to $x$. This is shown in Figure \ref{fig:mean_displacement_invariance}. Motivation for this assumption is discussed in Section \ref{eq:local_mean_displacement_invariance}. 
We approximate $\Phi(y,x) = \phi_x(y)$ by a weighted linear combination of the values $\phi_{x_i}(y - \mu(x) + \mu(x_i))$ for a collection of sample points $x_i$ near $x$. The weights are determined by preconditioned radial basis function interpolation.

The ability to rapidly evaluate approximate kernel entries $\Phi(y,x)$ allows us to construct an H-matrix approximation, $\boldsymbol{\Phi}_H$, of $\Phi$, using the conventional adaptive cross H-matrix construction method. In this method, one forms low-rank approximations of off-diagonal blocks of the matrix by sampling rows and columns of those blocks \cite{HACA}. We then use H-matrix methods to convert $\boldsymbol{\Phi}_H$ into an H-matrix approximation of $\Aop$, denoted $\mathbf{A}_H$. Schematically the overall H-matrix approximation proceeds as follows:
\begin{equation*}
\Aop \longrightarrow V, \mu, \Sigma \longrightarrow \{x_i\}_{i=1}^r \longrightarrow \{\impulseresponse_{x_i}\}_{i=1}^r \longrightarrow \boldsymbol{\Phi}_H \longrightarrow \mathbf{A}_H.
\end{equation*}
One may use H-matrix methods to perform further useful linear algebra operations involving $\mathbf{A}_H$, including matrix-matrix addition, matrix-matrix multiplication, matrix-vector products, matrix factorization, and matrix inversion. These H-matrix methods are fast and scale well to large problems. WHY DO THESE OPERATIONS: KRYLOV SOLVERS, SAMPLING STRATEGIES, CAN'T DO WITH A.

@@

We make the approximation that the support of $\impulseresponse_x$ is contained within the ellipsoid
\begin{equation}
\label{eq:support_ellipsoid}
E_x := \{x' \in \Omega: (x' - \spatialmean(x))^T \spatialcov(x)^{-1} (x' - \spatialmean(x)) \le \tau^2\},
\end{equation}
where $\tau$ is a fixed constant. The ellipsoid $E_x$ is the set of points within $\tau$ standard deviations from the mean of the Gaussian distribution with mean $\spatialmean(x)$ and covariance $\spatialcov(x)$, i.e., the Gaussian distribution which has the same mean and covariance as $\widehat{\impulseresponse}_x$.

@@

%In Section \ref{sec:intro} we noted that computing $\Aker\left(y,x\right)$ is computationally costly. 
%This section describes how we compute approximate kernel entries
%\begin{equation*}
%\widetilde{\Phi}(y,x) \approx \Phi(y,x)
%\end{equation*}
%for arbitrary pairs of points $(y,x) \in \Omega \times \Omega$. 
Given $(y,x)\in \Omega \times \Omega$, let
\begin{equation*}
	z_i := y - \mu(x) + \mu(x_i), \qquad i=1,\dots,k,
\end{equation*}
where $\{x_i\}_{i=1}^k$ are the $k$ nearest sample points to $x$, excluding sample points $x_i$ for which $z_i \notin \Omega$. Here $k$ is a small user defined parameter; e.g., $k=10$. Further, let
\begin{equation}
\label{eq:fxyxp}
f_i := \frac{V(x)}{V(x_i)}\phi_{x_i}\left(z_i\right), \qquad i=1,\dots,k,
\end{equation}
%for arbitrary pairs of points $(y,x) \subset \Omega \times \Omega$.
% while Section \ref{sec:approximate_kernel_entries} we showed how we can cheaply evaluate approximate kernel entries at arbitrary pairs of points $(y,x) \in \Omega \times \Omega$.
Note that $f_i$ is well-defined, because $\phi_{x_i}\left(z_i\right)$ is defined if and only if $z_i \in \Omega$, and $V(x_i)>0$ by our sample point picking procedure in Section \ref{sec:sample_point_selection}. We approximate $\Phi(y,x)$ by interpolating the (point,value) pairs
\begin{equation}
\left(x_i, f_i\right), \qquad i=1,\dots,k,
\end{equation}
at the point $x$. The idea is that $\Phi(y,x) = \phi_x(y) \approx \phi_{x_i}\left(z_i\right)$ per the discussion in Section \ref{eq:local_mean_displacement_invariance}, so we approximate $\Phi(y,x)$ by interpolating the values $\phi_{x_i}\left(z_i\right)$. The factor $\frac{V(x)}{V(x_i)}$ in \eqref{eq:fxyxp} preconditions the approximation to make it more robust if $V(x)$ varies widely.

>>>>

In this paper we form hierarchical matrix approximations, $\mathbf{A}_H$, of operators $\Aop$ that satisfy the following three properties:
\begin{description}
	\item[Locally supported impulse responses:] For all $x\in \Omega$, the support of $\impulseresponse_x$ is contained (or approximately contained) in a localized region.
	\item[Non-negative impulse responses:] We have
	\begin{equation*}
	\impulseresponse_x(y) \ge 0
	\end{equation*}
	for all (or approximately all) $(y,x) \in \Omega \times \Omega$.
	\item[Matrix-free:] One cannot easily evaluate kernel entries $\Aker(y,x)$. Instead, access to $\Aop$ is available through ``operator actions.'' That is, we have a black-box computational procedure (which is typically expensive) through which we may evaluate the maps
	\begin{equation*}
	u \mapsto\Aop u \quad \text{and} \quad v \mapsto \Aop^Tv
	\end{equation*} 
	for arbitrary functions $u$ and $v$. After discretization (see Appendix \ref{app:discretized_operations}), $\Aop$ becomes a dense matrix, $\bm{A}$, that is typically too large to be built and stored. This property is called ``matrix-free'' because at the discrete level it means that one can perform matrix-vector products of $\bm{A}$ and $\bm{A}^T$ with arbitrary vectors, but one cannot easily\footnote{One could compute $\bm{v} = \bm{A}\bm{e}_j$, where $\bm{e}_j=(0,\dots,0,1,0,\dots,0)$ is the unit vector which has $j^\text{th}$ component equal to one and all other components equal to zero, then extract $\bm{A}_{ij} = \bm{v}_i$. However, this process is wasteful because one computes the entire vector $\bm{v}$, then discards all but one component.} access matrix entries $\bm{A}_{ij}$. In applications, applying $\bm{A}$ to a vector may involve iteratively solving a large linear system, timestepping, or performing some other nontrivial computational procedure. 
	%For example, in reduced space approaches to PDE-constrained optimization and inverse problems, Hessian information is available only through the application of the Hessian to vectors, and one such Hessian application requires solving two PDEs \cite{HESSIANADJOINT}. 
\end{description} 
Once the hierarchical matrix approximation $\mathbf{A}_H$ is constructed, one may use H-matrix methods to perform further useful linear algebra operations involving $\mathbf{A}_H$, including matrix-matrix addition, matrix-matrix multiplication, matrix-vector products, matrix factorization, and matrix inversion. These H-matrix methods are fast and scale well to large problems. WHY DO THESE OPERATIONS: KRYLOV SOLVERS, SAMPLING STRATEGIES, CAN'T DO WITH A.

@@

The impulse response $\impulseresponse_x$ may be interpreted as a scaled probability distribution because of the non-negative impulse response property. Let $\spatialvol:\Omega \rightarrow \mathbb{R}$,
\begin{equation*}
\spatialvol(x) := \int_\Omega \impulseresponse_x(y) dy
\end{equation*}
denote the spatially varying scaling factor,
%, let 
%\begin{equation}
%\label{eq:scaled_impulse_response}
%\widehat{\impulseresponse}_x := \impulseresponse_x / \spatialvol(x)
%\end{equation}
%denote the normalized version of $\impulseresponse_x$. 
and let $\mu:\Omega \rightarrow \mathbb{R}^d$, $\Sigma:\Omega \rightarrow \mathbb{R}^{d \times d},$
\begin{equation*}
\spatialmean(x) := \mathbb{E}(\impulseresponse_x / V(x)), \qquad
\spatialcov(x) := \Var(\impulseresponse_x /V(x)),
\end{equation*}
to be the spatially varying mean and covariance of the normalized version of $\impulseresponse_x$, respectively. For each point $x$, imagine $\phi_x$ as a pile of sand. The scalar $V(x)$ is the mass of the sand pile, the vector $\mu(x)$ is the center of mass of the sand pile, and the matrix $\Sigma(x)$ contains information about how wide the sand pile is in each spatial direction. Throughout this paper we will use these spatially varying moment functions extensively.

\subsection{Local mean-displacement invariance}
\label{eq:local_mean_displacement_invariance}

Let $x$ and $x'$ be points in $\Omega$ that are ``close'' to each other, and consider the following four approximations, ordered by increasing level of sophistication:
\begin{align}
\phi_x(y) &\approx \phi_{x'}(y) \label{eq:translate1}\\
\phi_x(y) &\approx \phi_{x'}(y-x+x') \label{eq:translate2}\\
\phi_x(y) &\approx \phi_{x'}\left(y-\mu(x)+\mu(x')\right) \label{eq:translate3}\\
\phi_x(y)/V(x) &\approx \phi_{x'}\left(y-\mu(x)+\mu(x')\right) / V(x'). \label{eq:translate4}
%\frac{\phi_x(y)}{V(x)} &\approx \frac{\phi_{x'}\left(y-\mu(x)+\mu(x')\right)}{V(x')}. \label{eq:translate4}
\end{align}
Approximation \eqref{eq:translate1} says that $\phi_x$ can be approximated by $\phi_{x'}$ when $x$ and $x'$ are close. 
%This approximation follows from the assumption that $\Phi$ is smooth. 
Operators satisfying \eqref{eq:translate1} can be well-approximated via low-rank interpolative factorization/Nystrom approximation of $\Phi$ \cite{CUR,NYSTROM}.
% of the form
%\begin{equation}
%	\label{eq:low_rank_interpolation}
%	\Phi(y,x) \approx \sum_{i=1}^r w_i(x) \phi_{x_i}(y)
%\end{equation}
%where $\phi_{x_i}$ are known impulse responses at a collection of points $x_i$ scattered throughout $\Omega$, and $w_i$ are smooth weighting functions that interpolate the $\phi_{x_i}$. 
%In problems of practical interest, \eqref{eq:translate1} typically holds \emph{asymptotically} in the limit as $x'$ approaches $x$. 
However, 
%even if $\Phi$ is smooth (which is typically the case asymptotically),
%the relevant Lipschitz constant for continuity, and hence 
the required rank in the low rank approximation can be large, which makes algorithms based on \eqref{eq:translate1} computationally expensive. This is the case for Hessians in PDE constrained inverse problems with highly informative data, as discussed in Section \ref{sec:PDE_hessian_motivation}. 
%As the data become more informative, typically the ``mass'' of $\Phi(y,x)$ concentrates nearer and nearer to the ``diagonal'' $y=x$, the Lipschitz constant increases, and the required rank in the approximation increases.
%Moreover, if $\Aop$ is numerically low rank, then one would typically use more accurate and robust matrix-free methods for forming low-rank approximations, such as randomized SVD or Lanczos.

@@

Approximation \eqref{eq:translate3} improves upon \eqref{eq:translate1} and \eqref{eq:translate2}, and generalizes both. On one hand, if \eqref{eq:translate1} holds, then $\mu(x) \approx \mu(x')$, and so \eqref{eq:translate3} holds. On the other hand, translating a distribution translates its mean, so if \eqref{eq:translate2} holds, then $\mu(x')-\mu(x) \approx x' - x$, so again \eqref{eq:translate3} holds. But approximation \eqref{eq:translate3} can hold in situations where neither \eqref{eq:translate1} nor \eqref{eq:translate2} holds. For example, because the expected value commutes with affine transformations, \eqref{eq:translate3} will hold when an $\Aop$ is locally translation-invariant with respect to a rotated frame of reference, while \eqref{eq:translate2} will not hold in this case. Additionally, \eqref{eq:translate3} generalizes to operators $\Aop:L^2(\Omega_1) \rightarrow L^2(\Omega_2)'$ that map between function spaces on different domains $\Omega_1$ and $\Omega_2$, and even operators that map between domains with different spatial dimensions. In contrast, \eqref{eq:translate2} does not naturally generalize to operators that map between function spaces on different domains, because the formula $y-x+x'$ requires vectors in $\Omega_2$ and $\Omega_1$ to be added together.  We call \eqref{eq:translate3} ``local mean-displacement invariance,'' and illustrate \eqref{eq:translate3} in Figure \ref{fig:mean_displacement_invariance}.

We use approximation \eqref{eq:translate4}, which is the same as \eqref{eq:translate3}, except for the extra factors of $1/V(x)$ on the left hand side and $1/V(x')$ on the right hand side. These factors make the approximation more robust if $V(x)$ varies widely. Approximation \eqref{eq:translate4} is equivalent to \eqref{eq:translate3}, but with $\phi_x$ replaced by the its normalized version, $\phi_x/V(x)$. We call \eqref{eq:translate4} ``normalized local mean-displacement invariance.''

@@

Once the scattered impulse responses $\impulseresponse_{x_i}$ are computed, we approximate the integral kernel $\Phi(y,x)$ at arbitrary points $(y,x)$ by interpolation. The details of the interpolation will be described in Section \ref{sec:approximate_kernel_entries}, but the key principle behind the interpolation is the preconditioned local mean displacement invariance assumption discussed in Section \ref{eq:local_mean_displacement_invariance}.
%Specifically, we make the assumption that
%\begin{equation}
%\Phi(y,x) = \phi_x(y) \approx \phi_{x_i}(y - \mu(x) + \mu(x_i))
%\end{equation}
%if $x_i$ is close to $x$. This is shown in Figure \ref{fig:mean_displacement_invariance}. Motivation for this assumption is discussed in Section \ref{eq:local_mean_displacement_invariance}. 
We approximate $\Phi(y,x) = \phi_x(y)$ by a weighted linear combination of the values $\frac{V(x)}{V(x_i)}\phi_{x_i}(y - \mu(x) + \mu(x_i))$ for a collection of sample points $x_i$ near $x$. The weights are determined by preconditioned radial basis function interpolation.

The ability to rapidly evaluate approximate kernel entries $\Phi(y,x)$ allows us to construct an H-matrix approximation, $\boldsymbol{\Phi}_H$, of $\Phi$, using the conventional adaptive cross H-matrix construction method. In this method, one forms low-rank approximations of off-diagonal blocks of the matrix by sampling rows and columns of those blocks \cite{HACA}. We then use H-matrix methods to convert $\boldsymbol{\Phi}_H$ into an H-matrix approximation of $\Aop$, denoted $\mathbf{A}_H$. Schematically the overall H-matrix approximation proceeds as follows:
\begin{equation*}
\Aop \longrightarrow V, \mu, \Sigma \longrightarrow \{x_i\}_{i=1}^r \longrightarrow \{\impulseresponse_{x_i}\}_{i=1}^r \longrightarrow \boldsymbol{\Phi}_H \longrightarrow \mathbf{A}_H.
\end{equation*}

@@

We make the approximation that the support of $\impulseresponse_x$ is contained within the ellipsoid
\begin{equation}
\label{eq:support_ellipsoid}
E_x := \{x' \in \Omega: (x' - \spatialmean(x))^T \spatialcov(x)^{-1} (x' - \spatialmean(x)) \le \tau^2\},
\end{equation}
where $\tau$ is a fixed constant. The ellipsoid $E_x$ is the set of points within $\tau$ standard deviations from the mean of the Gaussian distribution with mean $\spatialmean(x)$ and covariance $\spatialcov(x)$, i.e., the Gaussian distribution which has the same mean and covariance as the normalized version of $\impulseresponse_x$.

@@

%In Section \ref{sec:intro} we noted that computing $\Aker\left(y,x\right)$ is computationally costly. 
%This section describes how we compute approximate kernel entries
%\begin{equation*}
%\widetilde{\Phi}(y,x) \approx \Phi(y,x)
%\end{equation*}
%for arbitrary pairs of points $(y,x) \in \Omega \times \Omega$. 
Given $(y,x)\in \Omega \times \Omega$, let
\begin{equation*}
	z_i := y - \mu(x) + \mu(x_i), \qquad i=1,\dots,k,
\end{equation*}
where $\{x_i\}_{i=1}^k$ are the $k$ nearest sample points to $x$, excluding sample points $x_i$ for which $z_i \notin \Omega$. Here $k$ is a small user defined parameter; e.g., $k=10$. Further, let
\begin{equation}
\label{eq:fxyxp}
f_i := \frac{V(x)}{V(x_i)}\phi_{x_i}\left(z_i\right), \qquad i=1,\dots,k,
\end{equation}
%for arbitrary pairs of points $(y,x) \subset \Omega \times \Omega$.
% while Section \ref{sec:approximate_kernel_entries} we showed how we can cheaply evaluate approximate kernel entries at arbitrary pairs of points $(y,x) \in \Omega \times \Omega$.
Note that $f_i$ is well-defined, because $\phi_{x_i}\left(z_i\right)$ is defined if and only if $z_i \in \Omega$, and $V(x_i)>0$ by our sample point picking procedure in Section \ref{sec:sample_point_selection}. We approximate $\Phi(y,x)$ by interpolating the (point,value) pairs
\begin{equation}
\left(x_i, f_i\right), \qquad i=1,\dots,k,
\end{equation}
at the point $x$. The idea is that $\Phi(y,x) = f_i$ per the discussion in Section \ref{eq:local_mean_displacement_invariance}, so we approximate $\Phi(y,x)$ by interpolating the values $f_i$.
